---
title: "Summary of AMF community assembly"
author: "Aidee Guzman"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: pdf_document
geometry: margin=2cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/Volumes/GoogleDrive/My Drive/Research/Research projects/Spatial project/Analysis/R workflow/fungalcommunitycomp")
## If pandoc is not working: https://stackoverflow.com/questions/58610380/rmarkdown-pandoc-error-after-update-to-macos-catalina-10-15
## https://holtzy.github.io/Pimp-my-rmd/

```

```{r include=FALSE, cache=FALSE}
## Source for Analysis workflow 

## *******************************************************
## 1. load
## *******************************************************
source("R scripts/load.R")

## *******************************************************
## 2. clean
## *******************************************************
source("R scripts/clean.R")

## *******************************************************
## 3. analysis
## *******************************************************
source("R scripts/analysis.R")

## *******************************************************
## 4. plots
## *******************************************************
source("R scripts/plots.R")


## *******************************************************
## 5. tables
## *******************************************************
source("R scripts/tables.R")



```

# Description of study design

Study design: farm type x block

* 21 sites: 10 monoculture and 11 polyculture

* 2 transects per 2 blocks (within-rows vs across-rows) each site

* 10 = 2017 and 11 =2018


\pagebreak

\tableofcontents 

\newpage  


\pagebreak  

# Drivers of AM compositional dissimilarity

## Crop diversity

**Plots** 
```{r, echo=FALSE, fig.align='center'}
final_ispline

```

**Model output**

```{r, tidy=TRUE, echo=FALSE}
as.data.frame(gdm_cd_wide)
```


\pagebreak  

## Farm type

**Plots** 
```{r, echo=FALSE, fig.align='center'}
final_ispline_ft

```

**Model output**

**Coefficents**
```{r, tidy=TRUE, echo=FALSE}
as.data.frame(gdm_ft_wide)
```

\pagebreak  

# MRM tests

## Crop divesrity

```{r, tidy=TRUE, echo=FALSE}
mrmTests
```

## Farm type
```{r, tidy=TRUE, echo=FALSE}
mrmTests_ft
```

## Environment
```{r, tidy=TRUE, echo=FALSE}
mrmTests_env
```

\pagebreak  


# Drivers of AMF alpha diversity

## Richness ~ crop diversity
**Plots** 
```{r, echo=FALSE, fig.align='center', fig.height=3.5}
effectSizes_richness_plot
```

**Whole farm**
```{r, tidy=TRUE, echo=FALSE}
modelSummary(all_wa_richness_cd)
```

**Within-rows**
```{r, tidy=TRUE, echo=FALSE}
modelSummary(all_w_richness_cd)
```

**Across-rows**
```{r, tidy=TRUE, echo=FALSE}
modelSummary(all_a_richness_cd)
```

## Shannon ~ crop diversity
**Plots** 
```{r, echo=FALSE, fig.align='center', fig.height=3.5}
effectSizes_shannon_plot
```

**Whole farm**
```{r, tidy=TRUE, echo=FALSE}
modelSummary(all_wa_shannon_cd)
```

**Within-rows**
```{r, tidy=TRUE, echo=FALSE}
modelSummary(all_w_shannon_cd)
```

**Across-rows**
```{r, tidy=TRUE, echo=FALSE}
modelSummary(all_a_shannon_cd)
```

## Richness ~ farm type
**Plots** 
```{r, echo=FALSE, fig.align='center'}
richness_ft_plots
```

**Whole farm**
```{r, tidy=TRUE, echo=FALSE}
modelSummary(all_wa_richness_ft)
```

**Within-rows**
```{r, tidy=TRUE, echo=FALSE}
modelSummary(all_w_richness_ft)
```

**Across-rows**
```{r, tidy=TRUE, echo=FALSE}
modelSummary(all_a_richness_ft)
```

## Shannon ~ farm type
**Plots** 
```{r, echo=FALSE, fig.align='center'}
shannon_ft_plots
```

**Whole farm**
```{r, tidy=TRUE, echo=FALSE}
modelSummary(all_wa_shannon_ft)
```

**Within-rows**
```{r, tidy=TRUE, echo=FALSE}
modelSummary(all_w_shannon_ft)
```

**Across-rows**
```{r, tidy=TRUE, echo=FALSE}
modelSummary(all_a_shannon_ft)
```

\pagebreak  

# AMF compositional differences between farm type

**Plots** 
```{r, echo=FALSE, fig.align='center'}
composition_plot
```

**Model output**
```{r, tidy=TRUE, echo=FALSE}
all_wa_composition$permanova
```

\pagebreak  

# dbRDA

**Plots** 
```{r, echo=FALSE, fig.align='center'}
dbRDA.plot
```

**Model output**
```{r, tidy=TRUE, echo=FALSE}
dbRDA_anova
```

\pagebreak  

# Variation partitioning

**Plots** 
```{r, echo=FALSE, fig.align='center'}
all_varPart_plot
mono_varPart_plot
poly_varPart_plot

```

**Model output**
```{r, tidy=TRUE, echo=FALSE}
as.data.frame(varpart_table_wide)
```

\pagebreak 

# Edaphic variables ~ crop diversity

**Plots** 
```{r, echo=FALSE, fig.align='center', fig.height=2}
env_plot_cd
```

**Model output**
```{r, tidy=TRUE, echo=FALSE}
edaphicModels_cd
```


\pagebreak  

# Edaphic variables ~ farm type

**Plots** 
```{r, echo=FALSE, fig.align='center', fig.height=2}
env_plot_ft
```

**Model output**
```{r, tidy=TRUE, echo=FALSE}
edaphicModels_ft
```

**mean +/- SE **
```{r, tidy=TRUE, echo=FALSE}
summaryDF
```

\pagebreak  


