---
title: "Summary of AMF community assembly"
author: "Aidee Guzman"
date: "7/23/2020"
output: pdf_document
geometry: margin=2cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/Volumes/GoogleDrive/My Drive/Research/Research projects/Spatial project/Analysis/R workflow/fungalcommunitycomp")
## If pandoc is not working: https://stackoverflow.com/questions/58610380/rmarkdown-pandoc-error-after-update-to-macos-catalina-10-15
## https://holtzy.github.io/Pimp-my-rmd/

```

```{r include=FALSE, cache=FALSE}
## Source for Analysis workflow 

## *******************************************************
## 1. load
## *******************************************************
source("R scripts/load.R")

## *******************************************************
## 2. clean
## *******************************************************
source("R scripts/clean.R")

## *******************************************************
## 3. analysis
## *******************************************************
source("R scripts/analysis.R")

## *******************************************************
## 4. plots
## *******************************************************
source("R scripts/plots.R")


## *******************************************************
## 5. tables
## *******************************************************
source("R scripts/tables.R")



```

# Description of study design

Study design: farm type x block

* 21 sites: 10 monoculture and 11 polyculture

* 2 transects per 2 blocks (focal vs non-focal) each site

* 10 = 2017 and 11 =2018


\pagebreak

\tableofcontents # adds table of contents

\newpage  


\pagebreak  

# local-rows

**Model output**
**Landscape scale**
```{r, tidy=TRUE, echo=FALSE}
landscape_AMF_f_table
```

**Local scale**
```{r, tidy=TRUE, echo=FALSE}
local_AMF_f_table
```


**Plots** 
```{r, echo=FALSE, fig.height = 4, fig.width = 6, fig.align='center'}
amf_f_plots
```

\pagebreak  


# landscape-rows
**Model output**
**Landscape scale**
```{r, tidy=TRUE, echo=FALSE}
landscape_AMF_n_table
```

**Local scale**
```{r, tidy=TRUE, echo=FALSE}
local_AMF_n_table
```


**Plots** 
```{r, echo=FALSE, fig.height = 4, fig.width = 6, fig.align='center'}
amf_n_plots
```

\pagebreak  

# Both landscape and local-rows

**Plots** 
```{r, echo=FALSE, fig.height = 4, fig.width = 6, fig.align='center'}
amf_n_plots
```

\pagebreak  


# Variance importance

**Output**
```{r, tidy=TRUE, echo=FALSE}
varianceImportance
```


**Plots** 
```{r, echo=FALSE, fig.height = 6, fig.width = 6, fig.align='center'}
varImp_plot

```

\pagebreak  


## Data summary

```{r, tidy=TRUE, echo=FALSE}
# mean +/- SE tables
summaryDF
```

