---
title: "Summary of AMF community assembly"
author: "Aidee Guzman"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: pdf_document
geometry: margin=2cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/Volumes/GoogleDrive/My Drive/Research/Research projects/Spatial project/Analysis/R workflow/fungalcommunitycomp")
## If pandoc is not working: https://stackoverflow.com/questions/58610380/rmarkdown-pandoc-error-after-update-to-macos-catalina-10-15
## https://holtzy.github.io/Pimp-my-rmd/

```

```{r include=FALSE, cache=FALSE}
## Source for Analysis workflow 

## *******************************************************
## 1. load
## *******************************************************
source("R scripts/load.R")

## *******************************************************
## 2. clean
## *******************************************************
source("R scripts/clean.R")

## *******************************************************
## 3. analysis
## *******************************************************
source("R scripts/analysis.R")

## *******************************************************
## 4. plots
## *******************************************************
source("R scripts/plots.R")


## *******************************************************
## 5. tables
## *******************************************************
# source("R scripts/tables.R")



```

# Description of study design

Study design: farm type x block

* 21 sites: 10 monoculture and 11 polyculture

* 2 transects per 2 blocks (focal vs non-focal) each site

* 10 = 2017 and 11 =2018


\pagebreak

\tableofcontents # adds table of contents

\newpage  


\pagebreak  

# Monoculture and Polyculture

**Model output**


**No-scale scale**
```{r, tidy=TRUE, echo=FALSE}
noscale$tables
```


**Landscape scale**
```{r, tidy=TRUE, echo=FALSE}
landscape_f$tables
```

**Local scale**
```{r, tidy=TRUE, echo=FALSE}
local_f$tables
```

\pagebreak  


# Focal blocks
**Model output**

## Monoculture

**Landscape scale**
```{r, tidy=TRUE, echo=FALSE}
landscape_mono_f$tables
```

**Local scale**
```{r, tidy=TRUE, echo=FALSE}
local_mono_f$tables
```

## Polyculture

**Landscape scale**
```{r, tidy=TRUE, echo=FALSE}
landscape_poly_f$tables
```

**Local scale**
```{r, tidy=TRUE, echo=FALSE}
local_poly_f$tables
```

\pagebreak  

**Plots for all focal blocks** 
```{r, echo=FALSE, fig.align='center'}
all_focal_plots
```

\pagebreak  



# Variance importance

**Output**
```{r, tidy=TRUE, echo=FALSE}
varImp_Focal
```


**Plots** 
```{r, echo=FALSE, fig.align='center'}
varImp_Focal_plot

```

\pagebreak  



# Mantel tests

## Composition

**Output**
```{r, tidy=TRUE, echo=FALSE}
mantel$table
```

**Plots** 
```{r, echo=FALSE, fig.align='center'}
mantel$plot
```

## Nestedness
**Output**
```{r, tidy=TRUE, echo=FALSE}
mantel_nestedness$table
```

**Plots** 
```{r, echo=FALSE, fig.align='center'}
mantel_nestedness$plot
```

## Turnover
**Output**
```{r, tidy=TRUE, echo=FALSE}
mantel_turnover$table
```

**Plots** 
```{r, echo=FALSE, fig.align='center'}
mantel_turnover$plot
```


# Monoculture

## Composition
**Output**
```{r, tidy=TRUE, echo=FALSE}
mono_mantel$table
```

**Plots** 
```{r, echo=FALSE, fig.align='center'}
mono_mantel$plot
```

## Nestedness
**Output**
```{r, tidy=TRUE, echo=FALSE}
mono_mantel_nestedness$table
```

**Plots** 
```{r, echo=FALSE, fig.align='center'}
mono_mantel_nestedness$plot
```

## Turnover
**Output**
```{r, tidy=TRUE, echo=FALSE}
mono_mantel_turnover$table
```

**Plots** 
```{r, echo=FALSE, fig.align='center'}
mono_mantel_turnover$plot
```


# Polyculture

## Composition
**Output**
```{r, tidy=TRUE, echo=FALSE}
poly_mantel$table
```

**Plots** 
```{r, echo=FALSE, fig.align='center'}
poly_mantel$plot
```

## Nestedness
**Output**
```{r, tidy=TRUE, echo=FALSE}
poly_mantel_nestedness$table
```

**Plots** 
```{r, echo=FALSE, fig.align='center'}
poly_mantel_nestedness$plot
```

## Turnover
**Output**
```{r, tidy=TRUE, echo=FALSE}
poly_mantel_turnover$table
```

**Plots** 
```{r, echo=FALSE, fig.align='center'}
poly_mantel_turnover$plot
```


\pagebreak  

